Differentially Private Bayesian Inference

### 2018-07-08 main.tex
fix bugs
rename file

\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
\label{sec_bayesInfer}
In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

\section{Algorithm Setting up}
\label{sec_setup}
For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_emgs}

% \subsubsection{Mechanism Set up}

In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{equation*}
\Delta_{g}u = 
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\hlg$ is monotonic, i.e. our utility function is monotonic.

% \subsubsection{Security Analysis}
% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
% \begin{equation*}
% \begin{split}
% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
% & =\frac
% {\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
% {\frac
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
% & = \left(\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp\left(\frac
% {\epsilon (u(x,r) - u(y,r))}
% {2 \Delta_{g}u}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & \leq
% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp(\epsilon).
% \end{split}
% \end{equation*}

% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

where local sensitivity is calculated by:

\begin{equation*}
\Delta_{l}u(x) = 
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.

\subsection{Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

\subsubsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$
which is similar to the exponential mechanism where we use
$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
summing up to $n+2$, as scoring function we use the Hellinger distance
from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
only difference is in the sensitivity part, since now we use the
smooth sensitivity.

\begin{definition} The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

@@

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

\subsubsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

@@

\textbf{Detail proof:}
\begin{itemize}

	\item $\lambda < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		\end{equation*}
	\item $\lambda > 0$

Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
\begin{equation*}
u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
\end{equation*}
By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
\begin{equation*}
\begin{split}
Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
\end{split}
\end{equation*}

In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
\begin{equation*}
\begin{split}
Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
\end{split}
\end{equation*}

When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.

\end{itemize}

@@

\subsubsection{Privacy Analysis}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

@@

\section{Accuracy Analysis}
\subsection{Laplace Mechanism}
Fixing a data set $x$, we will sample noise $Lap_i = floor(Y)$ where $Y \sim Lap(\frac{2}{\epsilon})$. Since already had the accuracy bound based on the $l_1$ norm in Laplace mechanism:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{2}}.
\end{equation*}

So we have the probability $Pr[| Lap_i |] = Pr[| Lap_i | \leq |Y| < | Lap_i | + 1] = e^{- \frac{| Lap_i | \epsilon}{2}} - e^{- \frac{(| Lap_i | + 1) \epsilon}{2}}$.

When we are in the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output. Then the probability of each group of noises are calculated as $Pr[\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}] = Pr[| Lap_1 | \leq |Y| < | Lap_1 | + 1] \times Pr[| Lap_2 | \leq |Y| < | Lap_2 | + 1] \times \cdots \times Pr[| Lap_{m-1} | \leq |Y| < | Lap_{m-1} | + 1] = (e^{- \frac{| Lap_1 | \epsilon}{2}} - e^{- \frac{(| Lap_1 | + 1) \epsilon}{2}}) \times (e^{- \frac{| Lap_2 | \epsilon}{2}} - e^{- \frac{(| Lap_2 | + 1) \epsilon}{2}}) \times \cdots \times (e^{- \frac{| Lap_{m-1} | \epsilon}{2}} - e^{- \frac{(| Lap_{m-1} | + 1) \epsilon}{2}})$.

% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
% \begin{equation*}
% \begin{split}
% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = \gamma
% \end{split} 
% \end{equation*}

\subsection{Exponential Mechanism with Global Sensitivity}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

\subsection{Exponential Mechanism with Smooth Sensitivity}
We explored three accuracy bounds for our exponential mechanism with smooth sensitivity.

First is the tight bound with very accurate calculation.
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] = \sum\limits_{\{z | \hlg(\bysinfer(x), z) \geq c\}} \frac{e^{\frac{- \epsilon \hlg(\bysinfer(x), z)}{S(x)}}}{NL_x}.
\end{equation*}

In order to be more efficient, we designed the second accuracy bound which is slightly looser than the first one:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{NL_x}.
\end{equation*}

In the second bound, we still need to calculate the normaliser every time. So we want make further improvements on efficiency like follows:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq \ \frac{|R| \exp{(\frac{- \epsilon c}{S(x)}})}{N(n)},
\end{equation*}
where we replace the $NL_x$ with a value only related to the size of the data. However, we haven't figured out the formula of this $N(n)$.

Within the three accuracy bounds, we will mainly use the first one in following analysis.

\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.

\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec. \ref{subsec_accuracy_hellinger}. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

\begin{itemize}

	\item In our exponential mechanism, the probability of outputting candidates wrt. steps (i.e., the hellinger distance) from the correct answer is calculated as:

	\begin{equation*}
	\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) = c] = \sum\limits_{\{z| \hlg(\bysinfer(x), z) = c\}}\frac{exp(\frac{- \epsilon c}{S(x)})}
	{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
	\end{equation*}

	Each candidate will occupy a portion of ``$1$'' as their outputting probability. Supposing candidates within three steps from the correct answer are good answers, the portion occupied by the good answers is decreasing when the size of candidate set increasing. That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing. More specifically, the candidate set size is $\sim n^{m-1}$, which means the probabilities of outputting good answers are decreasing with speed $\sim n^{m-1}$.

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d. So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:

	\begin{equation*}
	\begin{split}
	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
	\end{split}
	\end{equation*}
	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.

	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing. Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.

	\item Then, we do some concrete cases analysis.

	\begin{itemize}

		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
		 \hline
		\end{tabular}
		\end{center}

		Here, there are only 5 kinds of steps from correct answer. Our mechanism in the second column is clearly better than Laplace mechanism in the third column. When the candidates are close to correct answer (for example, $0, 1, 2$ steps from correct answer), our mechanism can output them with higher probabilities than Laplace mechanism. On the other hand, when candidates are far away from correct answer (for example, $3, 4$ steps), our mechanism can output them with lower probabilities.

		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
		 \hline
		 \multicolumn{3}{c}{$\cdots$}  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
		 \hline
		\end{tabular}
		\end{center}

		This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.

		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$. Some probabilities from the two mechanisms are listed as follows:
		% \begin{center}
		%  \begin{tabular}{c | c | c} 
		%  \hline
		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		%  \hline\hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
		%  \hline
		%  \multicolumn{3}{c}{$\cdots$}  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
		%  \hline
		% \end{tabular}
		% \end{center}

		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

	\end{itemize}

\end{itemize}

\begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

\subsubsection{Accuracy Analysis wrt. prior distribution}

\subsubsection{Accuracy Analysis wrt. data variance}

\section{Experimental Evaluations}
\label{experiment}

\subsection{Computation Efficiency}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

\subsection{Experimental Evaluations on Accuracy}
\label{subsec_experiment_accuracy}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}

>>>>

\section{Problem Statement}
Our research is based on an observation that under different measurement, mechanisms usually have different accuracy behavior. When adding noise according to a certain measurement, mechanism' accuracy behavior will be better than when adding noise according to other measurements. Here we study the private Bayesian inference based on Hellinger distance measurement. Showing that our newly-designed mechanism adding noise according to Hellinger distance performs better than baseline mechanism adding noise according to $l_1$ norm.

\section{Technical Problem Statement}
\label{sec_bayesInfer}

Our study based on the Bernoulli-Beta Bayesian inference. In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism. In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. The private posterior then will be $\dirichlet(\alpha_1 + n_1 + , \alpha_2 + n_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

\subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$
which is similar to the exponential mechanism where we use
$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
summing up to $n+2$, as scoring function we use the Hellinger distance
from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
only difference is in the sensitivity part, since now we use the
smooth sensitivity.

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

@@

\subsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

\subsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

@@

% \textbf{Detail proof:}
% \begin{itemize}

% 	\item $\lambda < 0$

% 		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
% 		\begin{equation*}
% 		\end{equation*}
% 	\item $\lambda > 0$

% Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
% \begin{equation*}
% u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
% \end{equation*}
% By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
% \begin{equation*}
% \begin{split}
% Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
% & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
% \end{split}
% \end{equation*}

% In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
% \begin{equation*}
% \begin{split}
% Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
% & = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
% & = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
% \end{split}
% \end{equation*}

% When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.

% \end{itemize}

@@

\subsection{Privacy Analysis}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}
